% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{email-marketing-campaign}{%
\section{\texorpdfstring{\textbf{Email Marketing
Campaign}}{Email Marketing Campaign}}\label{email-marketing-campaign}}

\textbf{Goal}

Optimizing marketing campaigns is one of the most common data science
tasks. Among the many marketing tools available, emails stand out as
particularly efficient.

Emails are great because they are free, scalable, and can be easily
personalized. Email optimization involves personalizing the content
and/or the subject line, selecting the recipients, and determining the
timing of the sends, among other factors. Machine Learning excels at
this.

\hypertarget{case-description}{%
\subsection{\texorpdfstring{\textbf{Case
Description}}{Case Description}}\label{case-description}}

The marketing team of an e-commerce site has launched an email campaign.
This site has email addresses from all the users who created an account
in the past.

They have chosen a random sample of users and emailed them. The email
lets the user know about a new feature implemented on the site. From the
marketing team perspective, success is if the user clicks on the link
inside of the email. This link takes the user to the company site.

You are in charge of figuring out how the email campaign performed and
were asked the following questions:

\begin{itemize}
\item
  \begin{quote}
  What percentage of users opened the email and what percentage clicked
  on the link within the email?
  \end{quote}
\item
  \begin{quote}
  The VP of marketing thinks that it is stupid to send emails in a
  random way. Based on all the information you have about the emails
  that were sent, can you build a model to optimize in future how to
  send emails to maximize the probability of users clicking on the link
  inside the email?
  \end{quote}
\item
  \begin{quote}
  By how much do you think your model would improve click through rate
  (defined as \# of users who click on the link/total users who receive
  the email). How would you test that?
  \end{quote}
\item
  \begin{quote}
  Did you find any interesting pattern on how the email campaign
  performed for different segments of users? Explain.
  \end{quote}
\end{itemize}

\hypertarget{data}{%
\subsection{\texorpdfstring{\textbf{Data}}{Data}}\label{data}}

We have 3 tables in this case study.Available
\href{https://drive.google.com/drive/folders/1LMRKLyoyKOal8LNYDL_w25sQY2tMv5mv?usp=drive_link}{\uline{here}}

The 3 tables are:

\textbf{email\_table} - info about each email that was sent

\textbf{Columns:}

\begin{itemize}
\item
  \begin{quote}
  \textbf{email\_id} : the Id of the email that was sent. It is unique
  by email.
  \end{quote}
\item
  \begin{quote}
  \textbf{email\_text} : there are two versions of the email: one has
  ``long text'' (i.e. has 4 paragraphs) and one has ``short text'' (just
  two paragraphs)
  \end{quote}
\item
  \begin{quote}
  \textbf{email\_version} : some emails were ``personalized'' (i.e. they
  had the name of the user receiving the email in the incipit, such as
  ``Hi John''), while some emails were ``generic'' (the incipit was just
  ``Hi,'').
  \end{quote}
\item
  \begin{quote}
  \textbf{hour} : the local time on which the email was sent.
  \end{quote}
\item
  \begin{quote}
  \textbf{weekday} : the day on which the email was sent.
  \end{quote}
\item
  \begin{quote}
  \textbf{user\_country} : the country where the user receiving the
  email was based. It comes from the user ip address when she created
  the account.
  \end{quote}
\item
  \begin{quote}
  \textbf{user\_past\_purchases} : how many items in the past were
  bought by the user receiving the email
  \end{quote}
\end{itemize}

\textbf{email\_opened\_table} - the id of the emails that were opened at
least once.

\textbf{Columns:}

\begin{itemize}
\item
  \begin{quote}
  \textbf{email\_id} : the id of the emails that were opened, i.e. the
  user clicked on the email and, supposedly, read it.
  \end{quote}
\end{itemize}

\textbf{link\_clicked\_table} - the id of the emails whose link inside
was clicked at least once.

\textbf{Columns:}

\begin{itemize}
\item
  \begin{quote}
  \textbf{email\_id} : if the user clicked on the link within the email,
  then the id of the email shows up on this table.
  \end{quote}
\end{itemize}

\end{document}
